### 2022-04-16 ms/ms.rmd
Seeting up MS. Need to think about how to best organise.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = TRUE, message = FALSE, warning = FALSE, tidy = TRUE, fig.width = 10)
## numbers >= 10^5 will be denoted in scientific notation,		  ## numbers >= 10^5 will be denoted in scientific notation,
  ## and rounded to 2 digits		  ## and rounded to 2 digits
  options(digits = 2)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = TRUE, message = FALSE, warning = FALSE, tidy = TRUE, fig.width = 10)
## numbers >= 10^5 will be denoted in scientific notation,		  ## numbers >= 10^5 will be denoted in scientific notation,
  ## and rounded to 2 digits		  ## and rounded to 2 digits
  options(digits = 2)

##################################
# Clean workspace
##################################
    rm(list=ls())

##################################
# Loading packages & Functions
##################################
    pacman::p_load(tidyverse, kableExtra, gridExtra, magrittr, Hmisc, googlesheets4, metafor, stringr, formatR, rmarkdown, kableExtra, flextable, raster, rasterVis, rnoaa, sp, ggmap, patchwork, ggpubr, RColorBrewer, sf, ggtree, ape, phytools, viridis, ncdf4.helpers, ncdf4, PCICt, readr, chron, tmap, rgdal, MCMCglmm, brms, latex2exp)

#devtools::install_github(repo = "ErikKusch/KrigR")
## Function to produce colour palette
# Note that temp is stored as a factor of 10 C larger, so needs to be divided. Also, we can greate a custom colour palelte function using colorRampPallette
colfunc <- colorRampPalette(rev(brewer.pal(10,"RdBu")))
#test colfunc(10) will generate the exact Hex codes for 10 different colours can 10 to 100 and you get 100 colour hex codes. Very useful webpage: https://pjbartlein.github.io/REarthSysSci/rasterVis01.html

    # loading functions
    source("../R/functions.R")

```
